### 2016-05-21 w-wires/paper_gerasimovda.tex
Updated paper, resolved todos

% \DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
% \DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

@@

\DeclareMathOperator\atanh{atanh}

@@

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
Since $s_1$ is concave \todo{proof? just take a look at second derivative?}, and strictly increasing, we can take any $Z_0 > Z$ and approximate the function by a piecewise linear function $s_4$:

@@

@@

\subsection*{Proofs of convergence for logarithmic parts}
\todo{DO NOT FORGET ABOUT shifted circle!!! $k = R \eexp{\iu t} + \iu C(R)$}

@@

\todo{Use some inequalities involving logarithms???}
% http://dlmf.nist.gov/4.5

@@

\todo{Use Schwartz inequality????}

@@

\todo{Calculate C(r) and R(r)}

@@

To make use of the inequality, we take

\todo{CONJUGATE!!!}
\begin{align*}
a    &= 0 \\
b    &= 2 \pi \\
f(t) &= \ln l(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g(t) &= \iu \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{align*}

\todo{Integral of $g(t)$ is estimated by $\pi$}

>>>>

% \DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand*\Eval[3]{\left.#1\right\rvert_{#2}^{#3}}
% \DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

@@

\DeclareMathOperator\atanh{atanh}
\DeclareMathOperator\atan{atan}

@@

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
Since $s_1$ is concave \todo{proof? just take a look at second derivative?}, and strictly increasing, we can take any $Z_0 > Z$ and approximate the function by a piecewise linear function $s_4$.

@@

For simplicity, take $Z_0 = Z + 1$, then:

\[
s_4(x + \iu y) = 
\begin{cases}
s_1(Z + 1) (y - Z) &, Z < y \le Z + 1 \\
s_1(Z + 1) &, y > Z + 1
\end{cases}
\]

@@

\subsection*{Proofs of convergence for logarithmic parts}

@@

@@

@@

Cayley transform: $W(z) = \frac{z - \iu}{z + \iu}$, inverse: $w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}$.

$C_r$ is the circle with radius $R(r) = \Im \frac{w(r) - w(-r)}{2}$ and center $C(r) = \Im \frac{w(r) + w(-r)}{2}$.

@@

To make use of the inequality, we take
\begin{align*}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln l(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \iu \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{align*}

\subsection*{Estimate of $\int \abs{g(t)}^2$}

\begin{align*}
\abs{g(t)}^2 = \abs{g^*(t)}^2
&=   \frac{\sqrt{R}^2}{\abs{R \cos t + \iu R \sin t + \iu C + i}^2} \\
&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
&= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1) \sin t} \\
&=   \frac{1}{R + (C + 1) \frac{C + 1}{R} + 2 (C + 1) \sin t} \\ 
\end{align*}

If we take $a = R + (C + 1) \frac{C + 1}{R}$, $b = 2 (C + 1)$, and notice $a > b$ \todo{Prove}, the integral is well known \todo{reference}:
\[
\int \frac{dx}{a + b \sin x} = \frac{2}{\sqrt{a^2 - b^2}} \atan \frac{a \tan \frac{x}{2} + b}{\sqrt{a^2 - b^2}}
\]

% Notice that since

\begin{align*}
a^2 - b^2
& =  (R + (C + 1) \frac{C + 1}{R})^2 - (2 (C + 1))^2\\
& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
& =  (R - (C + 1) \frac{C + 1}{R})^2 && \text{,and, since $C \ge R$} \\
&\ge (R - (R + 1) \frac{R + 1}{R})^2 \\
&\ge (2 + \frac{1}{R})^2 \\
&\ge 4
\end{align*}

We can choose the branch cut of the antiderivative in such a way that integration from $0$ to $2 \pi$ only affects a single Riemann sheet, therefore, we can use the fact that $\abs{\int\limits_a^b f(x) dx} \le \abs{F(b) - F(a)} \le \abs{F(a)} + \abs{F(b)}$.

Now, since $\frac{2}{\sqrt{a^2 - b^2}} \le \frac{2}{2} = 1$ and $\atan$ is bounded by $\frac{\pi}{2}$, by direct application of the fact above, we conclude that than $\pi$.
